\documentclass[10pt,a4paper]{extarticle}
\pagenumbering{gobble}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx}
\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\begin{document}
\begin{center}
    \begin{minipage}{\textwidth}
        \centering
        {\LARGE\textbf{Yusuf Okuducu}}\\[20pt]
        \href{mailto:yusuf@yusufokuducu.com}{yusuf@yusufokuducu.com} \quad
        \href{tel:+905398302718}{+90 539 830 2718} \quad
        \href{https://yusufokuducu.com}{yusufokuducu.com} \quad
        \href{https://linkedin.com/in/yusufokuducu}{in/yusufokuducu} \quad
        \href{https://github.com/yusufokuducu}{GitHub/yusufokuducu}
    \end{minipage}
\end{center}

\vspace{10pt}

\section{Summary}
I am a senior student at Necmettin Erbakan University, Department of Mathematics
and Computer Science. I have experience in various programming languages,
including Python, C, JavaScript, and Rust. I have developed projects in data science,
web development, cybersecurity, and game development. Through various technical
events and competitions, I have strengthened my problem-solving and application
development skills. I am focused on creating innovative solutions and continuously
improving myself.

\vspace{10pt}

\section{Certificates}
\textbf{Istanbul Data Science Academy} \hfill Remote\\
\textit{\href{https://istdatascience.com/certificate/DABYO237.pdf}{Google Cloud Data Analyst Bootcamp}}

\vspace{5pt}
\noindent\textbf{AI BUSINESS SCHOOL/Global AI Hub} \hfill Remote\\
\textit{Machine Learning Bootcamp}

\vspace{5pt}
\noindent\textbf{AI BUSINESS SCHOOL/Global AI Hub} \hfill Remote\\
\textit{Introduction to Machine Learning}

\vspace{10pt}

\section{Technical Skills}
\textbf{Programming Languages:} Python, C, C\#, Rust, GO, TypeScript, React, JavaScript\\
\textbf{Tools and Technologies:} Google Cloud Platform, FastAPI, Django, Next.js, SQLite, PostgreSQL, Git, GitHub, Linux, Shell Scripting, Unity, Docker, Kubernetes\\
\textbf{Abilities:} Data Analysis, Machine Learning, Data Visualization, SQL, Cybersecurity, API Development \& Integration, Game Development

\vspace{10pt}

\section{Projects}
\textbf{GitHub Portfolio:} \href{https://github.com/yusufokuducu}{GitHub/yusufokuducu}\\
My GitHub account where you can find my various projects.

\vspace{5pt}
\noindent\textbf{Personal Website:} \href{https://yusufokuducu.com}{yusufokuducu.com}

\vspace{5pt}
\noindent\textbf{\href{https://github.com/yusufokuducu/Image_Editor}{Image Editor}:} A lightweight yet powerful image editing tool with real-time filters, modern dark UI, and intuitive controls for quick image enhancement. \textit{Technologies: Python, CustomTkinter, OpenCV, Pillow}

\vspace{5pt}
\noindent\textbf{\href{https://github.com/yusufokuducu/Wifi-Scanner}{Network Scanner Suite}:} Comprehensive network scanning tools including WiFi and Bluetooth scanners with modern GUIs and advanced features. \textit{Technologies: Python, Scapy, CustomTkinter, asyncio}

\vspace{5pt}
\noindent\textbf{\href{https://github.com/yusufokuducu/GlobalAIHub_MCA}{Health Insurance Cost Predictor}:} A machine learning project for predicting health insurance costs using advanced data analysis techniques. \textit{Technologies: Python, pandas, scikit-learn, numpy, matplotlib}

\vspace{5pt}
\noindent\textbf{\href{https://github.com/yusufokuducu/Password_Generator}{Password Generator}:} A modern and user-friendly interface for generating secure, customizable passwords with advanced entropy measures. \textit{Technologies: Python, CustomTkinter}

\vspace{5pt}
\noindent\textbf{\href{https://github.com/yusufokuducu/BC-EventCard}{BC-EventCard}:} A blockchain-based, decentralized event ticket creation and management system. \textit{Technologies: React, Solidity, Hardhat, TailwindCSS, Next.js}

\vspace{5pt}
\noindent\textbf{\href{https://github.com/yusufokuducu/gochat}{Gochat}:} A real-time chat application developed using Go and WebSockets. \textit{Technologies: Go, WebSocket, JavaScript, HTML, CSS}

\vspace{10pt}

\section{Education}
\textbf{Necmettin Erbakan University \textit{(Faculty of Science)}} \hfill 2021 -- Present\\
\textit{Department of Mathematics and Computer Science, 4th year}

\vspace{5pt}
\noindent\textbf{Adana Middle East College} \hfill 2018 -- 2019\\
\textit{Department of Mathematics}

\end{document}